---
title: "DDS Group Project"
author: "Chad Reo & Sophia Wu & Clifford Otun"
date: "7/4/2020"
output: html_document
---
```{r}
#Load Libraries and Data
library(caret)
library(class)
library(dplyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(Hmisc)
library(jsonlite)
library(kableExtra)
library(knitr)
library(maps)
library(naniar)
library(stringr)
library(tidyr)
library(tidyverse)
library(usmap)

```

##1. Number of Breweries Per State
#merged Data first
## The number of breweries pr state ranges between 1 and 40 with an exceptional case of 47 in Colordo.  
## As seen from the map, the number increases with increase in the darckness of the color associated with each state.  
```{r}
#breweries <- read.csv("Breweries.csv")
#beer<- read.csv("Beers.csv")
breweries = read.csv("C:/Users/chadr/OneDrive/Documents/MS_DS_SMU/6306 Doing Data Sci/Unit8/Breweries.csv")
beers<- read.csv("C:/Users/chadr/OneDrive/Documents/MS_DS_SMU/6306 Doing Data Sci/Unit8/Beers.csv")
40
```
#2. Merge Beer Data with Brewery  Data
##  The data was obtained in two parts, the beer data and the brewery data. Both files were merged to obtain a common  
##  data for which analysis was carried out to address the needs of Budweiser.  
```{r}
beerBrew=merge(beers,breweries,by.x="Brewery_id",by.y="Brew_ID")
beerBrew$Brewery_id = as.factor(beerBrew$Brewery_id)
beerBrew$Beer_ID = as.factor(beerBrew$Beer_ID)

#add in map data
#add in map data
stateCoords=us_map()
# Remove Leading Spaces from State Column of merged Beer Brew Data frame (prepare for join)
beerBrew$State = gsub(" ","",beerBrew$State)
#str(beerBrew)

# Summarise Each State's Number of Breweries and Beers
stateBrewBeer1 = beerBrew %>% 
  select(State, Brewery_id) %>% 
  group_by(State, Brewery_id) 
stateBrewBeer2 = stateBrewBeer1 %>% distinct(State, Brewery_id) 
stateBrewBeer3 = stateBrewBeer2 %>%  group_by(State) %>% tally()
stateBrewBeer3$state = stateBrewBeer3$State 
str(stateBrewBeer3)

stateBrewBeer4 = beerBrew %>% 
  select(State, Beer_ID) %>% 
  group_by(State, Beer_ID) 
stateBrewBeer5 = stateBrewBeer4 %>% distinct(State, Beer_ID) 
stateBrewBeer6 = stateBrewBeer5 %>%  group_by(State) %>% tally()

StatebeerBrew=merge(stateBrewBeer6,stateBrewBeer3,by.x="State",by.y="State")

#rename counts
colnames(StatebeerBrew)[2] <-"Beers"
colnames(StatebeerBrew)[3] <-"Breweries"

#put in DataFrame for table
#on ppt
map_view_df = StatebeerBrew[order(StatebeerBrew$Breweries),] %>% select(state, Count = Breweries) 
view(head(map_view_df,26))  
view(tail(map_view_df,25)) 


#put in nice little map
#on ppt
plot_usmap(data=map_view_df,values="Count",labels = TRUE, offset=0.5, color = "red")  +
  scale_fill_continuous(low = "white", high = "red", name="Number Breweries")+ 
  theme(legend.position = "right") +
  labs(title = "Brewery Count",
       subtitle = "Darker Areas have the Most Breweries") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))

```
#3. Address the missing values in each column.  
## Due to the amount of data obtained, a percentage was selected for the analysis.  
## The data also as missing information probably as a result of a lack in variety.  
```{r}
#3. Address the missing values in each column.
# plot missing values in each column, rename some columns
#on ppt
gg_miss_var(beerBrew)
gg_miss_var(beerBrew %>% select(IBU,ABV, State), State)
gg_miss_var(beerBrew %>% select(IBU,ABV, State), State, show_pct = TRUE)

ggplot(beerBrew,
       aes(x = IBU,
           y = ABV)) +
  geom_miss_point() + labs(title = "Plot of Values") + theme_light()

# convert empty string Styles to NAs to more easily see missings in all columns
beerBrew$Style[which(beerBrew$Style=="")]=NA
view(sapply(beerBrew, function(x) sum(is.na(x))))

```
#4.Compute the median alcohol content and international bitterness unit for each state. 
#Plot a bar chart to compare.
```{r}
beerBrew %>% filter(!is.na(ABV)) %>%
 group_by(State) %>%
  summarise(ABV=median(ABV)) %>%
  ggplot(aes(x=reorder(State,-ABV),ABV)) +
  geom_bar(stat="identity", position="dodge", color='skyblue',fill='darkred') + 
  # scale_y_continuous(limits = c(0.5,0.07))+
  coord_flip()+ 
  xlab("State") +  ylab("ABV") + ggtitle("Median ABV by State") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))+ 
  theme(text = element_text(size=8,color= 'black'))


beerBrew %>% filter(!is.na(IBU)) %>%
  group_by(State) %>%
  summarise(IBU=median(IBU)) %>%
  ggplot(aes(x=reorder(State,-IBU),IBU)) +
  geom_bar(stat="identity", position="dodge", color='skyblue',fill='darkred') + 
  coord_flip()+ 
  xlab("State") +  ylab("IBU") + ggtitle("Median IBU by State") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))+ 
  theme(text = element_text(size=8,color= 'black'))
```
#5. (part 1) Which state has the maximum alcoholic (ABV) beer? 
#Which state has the most bitter (IBU) beer?
## The state with the maximum ABV was found to be Colorado  
## and that with the maximum IBU was found to be Oregon  
```{r}
#find the single most ABV beer
beerBrew %>% filter(!is.na(ABV)) %>% mutate(maxABV=max(ABV)) %>%
  filter(ABV==maxABV) %>% select(State, Name.x, Name.y, ABV)

beerBrew %>% filter(!is.na(ABV)) %>% mutate(minABV=min(ABV)) %>%
  filter(ABV==minABV) %>% select(State, Name.x, Name.y, ABV)

beerBrew %>% filter(!is.na(IBU)) %>% mutate(maxABV=max(IBU)) %>%
  filter(IBU==maxABV) %>% select(State, Name.x, Name.y, IBU)

beerBrew %>% filter(!is.na(IBU)) %>% mutate(minIBU = min(IBU)) %>%
  filter(IBU==minIBU) %>% select(State, Name.x, Name.y, IBU)


#find the single most bitter beer
beerBrew %>% filter(!is.na(IBU)) %>% mutate(maxIBU=max(IBU)) %>%
  filter(IBU==maxIBU)%>%select(State,Name.x,Name.y,IBU)

```
#6.Comment on the summary statistics and distribution of the ABV variable
#The ABV is mostly normally distributed with a noticeable right tail.  
#The mean is Larger than the median.
```{r}
ggplot(data=beerBrew, aes(x = State, y = ABV)) +
  geom_boxplot(col = "red", fill="pink") + coord_flip() +
  geom_jitter(position=position_jitter(0.05),col="blue") +
  theme_bw(base_size = 14) +
  xlab("State") +  ylab("ABV") + ggtitle("ABV Stats by State") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))+ 
  theme(text = element_text(size=8,color= 'black'))

ggplot(data=beerBrew, aes(x = State, y = IBU)) +
  geom_boxplot(col = "red", fill="pink") + coord_flip() +
  geom_jitter(position=position_jitter(0.05),col="blue") +
  theme_bw(base_size = 14) +
  xlab("State") +  ylab("IBU") + ggtitle("IBU Stats by State") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))+ 
  theme(text = element_text(size=8,color= 'black'))



#Check for normality of ABV using qq plot and histogram
#on ppt
beerBrew %>% filter(!is.na(ABV)) %>% select(ABV)%>%summary()

gridExtra::grid.arrange(
beerBrew %>% filter(!is.na(ABV)& ABV > .001) %>% ggplot(aes(x=ABV))+ 
  geom_histogram(aes(y=..density..), colour="black", fill="blue")+
  geom_density(alpha=.5, fill="#FF6666") + 
  geom_vline(aes(xintercept=mean(ABV)),
             color="red", linetype="dashed", size=1) +
  geom_vline(aes(xintercept=median(ABV)),
             color="black", linetype="dashed", size=1) +
  labs(y = "Density") + labs(x = "ABV") +
  ggtitle("Checking Normaily of ABV", subtitle = "Black line = Median and Red line = Mean") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue")),


beerBrew %>% filter(!is.na(ABV) & ABV > .001) %>% ggplot(aes(x=log(ABV)))+ 
  geom_histogram(aes(y=..density..), colour="black", fill="blue")+
  geom_density(alpha=.5, fill="#FF6666") + 
  geom_vline(aes(xintercept=mean(log(ABV))),
             color="red", linetype="dashed", size=1) +
  geom_vline(aes(xintercept=median(log(ABV))),
             color="black", linetype="dashed", size=1) +
    labs(y = "Density") + labs(x = "ABV") +
  ggtitle("Checking Normaily of Log ABV", subtitle = "Black line = Median and Red line = Mean") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue")),
nrow  = 1
)

gridExtra::grid.arrange(
beerBrew %>% filter(!is.na(ABV) & ABV > .001) %>% ggplot(aes(sample=ABV)) +stat_qq() + stat_qq_line(color = "red") + ggtitle("QQ Plot of ABV")+ 
  theme(panel.background = element_rect(color = "black", fill = "lightblue")),
beerBrew %>% filter(!is.na(ABV) & ABV > .001) %>% ggplot(aes(sample=log(ABV))) + stat_qq() + stat_qq_line(color = "red") + ggtitle("QQ Plot of Log ABV")+ 
  theme(panel.background = element_rect(color = "black", fill = "lightblue")),
nrow  = 1
)
```
#7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.  Make your best judgment of a relationship and EXPLAIN your answer.
#There is a moderate positive correlation between ABV and IBU.  
#The upward slope is evidence of a positive relationship.  The points' moderate to small deviations from the trendline is clear evidence of a moderate to weak relationship.
```{r}
#Categorize the many styles into 7 groups
beerBrew$StyleCat= case_when(
  grepl( "Ale",beerBrew$Name.x) ~ "Ale",
  grepl("(India Pale Ale|IPA)",beerBrew$Name.x) ~ "IPA",
  grepl("Lager",beerBrew$Name.x)~"Lager",
  grepl("Stout",beerBrew$Name.x)~"Stout",
  grepl("Porter",beerBrew$Name.x)~"Porter",
  grepl("Cider",beerBrew$Name.x)~"Cider",
  grepl("Pilsner",beerBrew$Name.x)~"Pilsner",
  TRUE~"Other"
)


beerBrew$StyleCat2 =   case_when(
  grepl( "Ale",beerBrew$Style) ~ "Ale",
  grepl("(India Pale Ale|IPA)",beerBrew$Style) ~ "IPA",
  grepl("Lager",beerBrew$Style)~"Lager",
  grepl("Stout",beerBrew$Style)~"Stout",
  grepl("Porter",beerBrew$Style)~"Porter",
  grepl("Cider",beerBrew$Style)~"Cider",
  grepl("Pilsner",beerBrew$Style)~"Pilsner",
  TRUE~"Other"
)

beerBrew$StyleCat3 =   case_when(beerBrew$StyleCat == "Other" ~ beerBrew$StyleCat2, TRUE ~ beerBrew$StyleCat)

beerBrew %>% filter(!is.na(ABV)&!is.na(IBU))%>%
  ggplot(aes(ABV,IBU,color=StyleCat3))+
  geom_point(position=position_jitter(width=0.01),alpha=0.5)+
  geom_smooth(method="lm",se=FALSE,size=2) +
  labs(title="Correlation Between ABV and IBU") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))
  

beerBrew %>% filter(!is.na(ABV)&!is.na(IBU))%>%
  ggplot(aes(ABV,IBU,color=StyleCat3))+
  geom_point(position=position_jitter(width=0.01),alpha=0.5)+
  geom_smooth(method="lm",se=FALSE,size=2) +
  facet_wrap(~StyleCat3) +
  labs(title="Correlation Between ABV and IBU", subtitle = "Broken out by Beer Style") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))

```
#8.1 Group beer styles into larger style buckets
#Categorize the many styles into 5 groups
```{r transform data beers.csv}
beers2 <- beers
colnames(beers2)
names(beers2) <- c("beername", "beerID", "beerABV", "beerIBU", "beer.brewery.id", "beerstyle", "beerOunce")
head(beers2)

```

```{r transform data breweries.csv}
brew2 <- breweries
colnames(brew2)
names(brew2) <- c("brewery.id", "brewery.name", "brewery.city", "brewery.state.abb")

brew2 <- brew2 %>%
  mutate(brewery.state.abb = trimws(brewery.state.abb))

head(brew2)

```

#Insert State name and region

```{r Add state abb,name,region}
#makes a data frame with State abbreviation, name  and region
stateinf= data.frame(state.abb, state.name, state.region, state.x77, stringsAsFactors=FALSE) 
head(stateinf[1:5])


```
#Merge data brew2 with data stateinf and calculate breweries numbers are present in each state

```{r brewery count}

brewstate<- merge(brew2, stateinf[1:5], by.x = "brewery.state.abb", by.y = "state.abb", all.x = TRUE)

head(brewstate)


```


```{r merge data beers and breweries}

beermerged <- merge(beers2, brewstate, by.x = "beer.brewery.id", by.y = "brewery.id")

```


```{r add column beeripaale into the combined beer form}

beermerged$beeripaale<- ''

head(beermerged)

```


```{r Get all different beers styles numbers}
#Get all different beers styles' numbers
beermerged %>%count(beerstyle)
```


```{r missing value}
#filter missing value
beermerged %>%
  filter(beerstyle == '')

```


```{r IPA beers}

beermerged %>%
  filter(beerstyle %in% c("American Double / Imperial IPA", "American IPA", "Belgian IPA", "English India Pale Ale (IPA)")) %>%
  count(beerstyle)

beeripa <- beermerged %>%
  filter(beerstyle %in% c("American Double / Imperial IPA", "American IPA", "Belgian IPA", "English India Pale Ale (IPA)")) %>%
  mutate(beeripaale= 'IPA')


head(beeripa)
```



```{r other Ale beer}

# Kilt Lifter Scottish-Style Ale (1635)
beermerged[946,]

beermerged %>%
  filter(!beerstyle %in% c("American Double / Imperial IPA", "American IPA", "Belgian IPA", "English India Pale Ale (IPA)")) %>%
  filter(str_detect(beerstyle, "Ale") |  beerID==1635) %>%
  count(beerstyle)

beerale <- beermerged %>%
  filter(!beerstyle %in% c("American Double / Imperial IPA", "American IPA", "Belgian IPA", "English India Pale Ale (IPA)")) %>%
  filter(str_detect(beerstyle, "Ale") |beerID==1635) %>%
  mutate(beeripaale= 'Ale')

head(beerale)

```


```{r boundry words}

head(beermerged) %>%
  mutate(beer.style.words = as.character(str_split(beerstyle, boundary("word")))) %>%
  select(beer.style.words)


```

```{r regex}

# India Pale Ale
IPA <- c("American Double / Imperial IPA", "American IPA", "Belgian IPA", "English India Pale Ale (IPA)")


```



```{r combine beer IPA and Ale}

total_beers_count <- dim(beermerged)[1]
ipa_count <- dim(beeripa)[1]
ale_count <- dim(beerale)[1]

beercombined_ale <- rbind(beeripa, beerale)

ipa_ale_count <- dim(beercombined_ale)[1]


head(beercombined_ale)

```


```{r Boxplot of ABU between IPA and other Ale}

beercombined_ale %>% 
  filter(!is.na(beerABV)) %>%
  ggplot(aes(x =beeripaale, y =beerABV, fill = beeripaale)) + 
  geom_boxplot() + 
  ggtitle("Boxplot of ABU between IPA and other Ale") + 
  xlab("Style") + 
  ylab("ABV")+ 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))

```
  
 
 
```{r Boxplot of IBU between IPA and other Ale}

beercombined_ale %>% 
  filter(!is.na(beerIBU)) %>%
  ggplot(aes(x = beeripaale, y =beerIBU, fill = beeripaale)) + 
  geom_boxplot() + 
  ggtitle("Boxplot of IBU between IPA and other Ale") + 
  xlab("Style") + 
  ylab("IBU")+ 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))

```
```{r}
beerclassify <- beercombined_ale %>% 
  filter(!is.na(beerABV) & !is.na(beerIBU) & !is.na(Population) & !is.na(Income))

beerclassify %>%
  group_by(beeripaale) %>%
  summarise(beers.abv.median = median(beerABV), beers.ibu.median = median(beerIBU), count = n())


beerclassify %>% 
  ggplot(aes(x = beerABV, y = beerIBU, color =  beeripaale)) + 
  xlab("ABV") + ylab("IBU") + 
  geom_point()+ 
  ggtitle("Classifying Beers Using ABV and IBU") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))
```
 
```{r}
library(class)
library(caret)
library(e1071)
library(purrr)

#use KNN classification to investigate the beer type with respect to IBV and ABU between IPA and ALE
set.seed(300)
split.perc = .70

train.indices = sample(1:dim(beerclassify)[1],round(split.perc * dim(beerclassify)[1]))

train = beerclassify[train.indices,]
test = beerclassify[-train.indices,]

dim(beerclassify) 
dim(train) 
dim(test)
#use IBV and ABU variables to get beerIPAale type accuracy
classifications = knn(train[,c(4,5)],test[,c(4,5)], train$beeripaale, prob = TRUE, k = 10)
confusionMatrix(table(test$beeripaale,classifications))

# use ABV and Income two variables to check beerIPAale type accuracy,then compare it with the above original one
classifications = knn(train[,c(5,14)],test[,c(5,14)], train$beeripaale, prob = TRUE, k = 17)
confusionMatrix(table(test$beeripaale,classifications))


```


## Loop for many k and one training / test partition
```{r}
acc = data.frame(accuracy = numeric(30), k = numeric(30))

for(i in 1:30)
{
  classifications = knn(train[,c(4,5)],test[,c(4,5)], train$beeripaale, prob = TRUE, k = i)
  table(test$beeripaale, classifications)
  CM = confusionMatrix(table(test$beeripaale,classifications))
  acc$accuracy[i] = CM$overall[1]
  acc$k[i] = i
}

plot(acc$k,acc$accuracy, type = "l", main = "Investigation of beer type with IBU&ABV",xlab = "K Value", ylab="Accuracy")

```
## Loop for many k and many training / test partitions
```{r}

set.seed(100)
iterations = 100
numks = 25


masterAcc = matrix(nrow = iterations, ncol = numks)

for(j in 1:iterations)
{
  train.indices = sample(1:dim(beerclassify)[1],round(split.perc * dim(beerclassify)[1]))
  train = beerclassify[train.indices,]
  test = beerclassify[-train.indices,]
  for(i in 1:numks)
  {
    classifications = knn(train[,c(4,5)],test[,c(4,5)], train$beeripaale, prob = TRUE, k = i)
    table(test$beeripaale, classifications)
    CM = confusionMatrix(table(test$beeripaale,classifications))
    masterAcc[j,i] = CM$overall[1]
  }
  
}

MeanAcc = colMeans(masterAcc)

plot(seq(1,numks,1),MeanAcc, type = "l",main = "Investigation of beer type with IBU&ABV",xlab = "K value",ylab="Beer type accuracy")

which.max(MeanAcc)
max(MeanAcc)


```
```{r  check correlation within IBU,ABV,Income, population,Ounce}
#check multicorrelation within IBU,ABV,Income, population, ounce
library(tidyverse)
library(corrplot)
library(RColorBrewer)
library(ggplot2)
library(GGally)

#Replace missing value with mean
beermerged1<- beermerged
beermerged1$beerABV[which(is.na(beermerged1$beerABV))] <- mean(beermerged1$beerABV,na.rm=TRUE)
beermerged1$beerIBU[which(is.na(beermerged1$beerIBU))] <- mean(beermerged1$beerIBU,na.rm=TRUE)


filterbeermerged <-beermerged1 %>% select(beerIBU,beerABV, beerOunce,Income, Population) 

ggpairs(filterbeermerged, title="correlogram with ggpairs()") 
corrplot(cor(filterbeermerged), type="upper", order="original")

```
#9 Knock their socks off!  Find one other useful inference from 
#the data that you feel Budweiser may be able to find value in.

```{r}
###Get population


#go get Key from USCensus
US_Census_KEY = "3094ca397d1d50a4e3a230346dbaf7d801f753d4" #get from US Census website

#Pull Json data
Json <- "https://api.census.gov/data/2018/acs/acs1?get=NAME,B01001_001E&for=state:*"


#put in Dataframe
get_json <- jsonlite::fromJSON(Json, flatten = TRUE)
str(get_json)
Pop_df <- as.data.frame(get_json)
str(Pop_df)
colnames(Pop_df)
head(Pop_df)

#clean up by renaming columns and dropping unneeded columns/rows
names(Pop_df)[1] <- "State"
names(Pop_df)[2] <- "Population"
head(Pop_df)

#clean up by dropping unneeded columns/rows
Pop_df <- select(Pop_df, -3)
Pop_df <- Pop_df[-c(1),]

#change factor to numeric
Pop_df$Population <- as.numeric(as.character(Pop_df$Population))

view(Pop_df)
head(Pop_df)
summary(Pop_df)
```

```{r}
#take a look at data
Pop_df[order(Pop_df$Population),]

#graph Population
#in ppt
library(scales)
Pop_df  %>% 
  ggplot(aes(x = reorder(State, -Population), y = Population)) +
  geom_bar(stat = "identity", fill = "darkred") + 
  #theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6)) +
  labs(title = "2018 US Population by State",
       subtitle = "Source:  US Census API") + 
  xlab("State") + coord_flip() + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))+
   theme(text = element_text(size=8,color= 'black'))


```

```{r}
#pull out abbr from Coordinates map
StateNames <- stateCoords %>% select(abbr, full) %>% distinct(abbr, full)

#get style count by State
StyleCnt <- beerBrew %>% mutate(State=gsub(" ","",State)) %>%
  select(State, StyleCat3) %>% 
  filter(!is.na(StyleCat3)) %>% group_by(State, StyleCat3) %>% tally( name = "Count")

#add Abbr to State Names
StatePop = merge(StateNames,Pop_df,by.x="full",by.y="State")

#Merge Population and Beer Data
Revenue_DF = merge(StatePop,StatebeerBrew,by.x="abbr",by.y="state")
str(Revenue_DF)
Revenue_DF[order(Revenue_DF$Beers/log(Revenue_DF$Population)),]



#add metrics
Revenue_DF = Revenue_DF %>% mutate(LogPop = log(Population),
                                   brewsPerLogPop = Beers/log(Population),
                                   beersPerLogPop = Beers/log(Population))

colnames(Revenue_DF)[1] <- "state"
#put in DataFrame for table

Revenue_DF[order(Revenue_DF$beersPerLogPop),] 

#put in map
plot_usmap(data=Revenue_DF,values="beersPerLogPop",labels = TRUE, offset=0.5, color = "red")  +
  scale_fill_continuous(type = "viridis", name="Beers per capita") + 
  theme(legend.position = "right") +
  labs(title = "Beer Density",
       subtitle = "Darker Areas have the Fewest Beers per capita") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))
```

```{r}
#Regression Line
#Look at data points with high residual error
#in ppt
Revenue_DF %>% filter(beersPerLogPop < 7.5) %>% 
  ggplot(aes(LogPop,beersPerLogPop)) +
  geom_point(position=position_jitter(width=0.01),alpha=0.5)+
  geom_smooth(method="lm",se=FALSE,size=2) +
  labs(title="Correlation between Population and Count of Beers") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))+
  labs(y = "Beers per Log of US Population") + labs(x = "Log of US Population")



#get low values as areas to focus
#in ppt
TargetStates <- Revenue_DF %>% filter(beersPerLogPop <= 2,
  LogPop > 15) %>% 
  select(State = full, Population, BeerFactor = beersPerLogPop)
                
view(TargetStates)



```

```{r}
#which kind of beer to sell
StyleCnt$StyleCat3 <- as.factor(StyleCnt$StyleCat3)
StyleCnt$State <- as.factor(StyleCnt$State)

#str(StyleCnt)


StyleTotals <- StyleCnt %>% group_by(StyleCat3) %>% summarise(Total = sum(Count))

StyleTotals$BeerFactor <- StyleTotals$Total/sum(Revenue_DF$LogPop)


TargetStates_LogPop <- Revenue_DF %>% filter(State == "AR" | State == "MS" |State == "AL" | 
                                           State == "GA" |State == "SC" | State == "TN" ) %>%
                      select(LogPop) %>%  sum(Revenue_DF$LogPop)
str(TargetStates_LogPop)


#get style count by State
TargetStates_StyleCnt <- beerBrew %>% filter(State == "AR" | State == "MS" |State == "AL" | 
                                               State == "GA" |State == "SC" | State == "TN" ) %>%
  mutate(State=gsub(" ","",State)) %>%
  select(State, StyleCat3) %>% 
  filter(!is.na(StyleCat3)) %>% group_by(StyleCat3) %>% tally( name = "Totals")


TargetStates_StyleCnt$BeerFactor <- TargetStates_StyleCnt$Totals/TargetStates_LogPop



#Show Which Beers to Sell
#in ppt
gridExtra::grid.arrange(

StyleTotals %>% ggplot(aes(StyleCat3,BeerFactor)) + 
  geom_point(shape = 21, colour = "black", fill = "red", size = 5, stroke = 5)+
  labs(title="Plotting Beer Factor by Style Accross the US") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))+
  labs(y = "Beer Factor") + labs(x = "Beer Style"),

TargetStates_StyleCnt %>% ggplot(aes(StyleCat3,BeerFactor)) + 
  geom_point(shape = 21, colour = "black", fill = "red", size = 5, stroke = 5)+
  labs(title="Plotting Beer Factor by Style in Target States") + 
  theme(panel.background = element_rect(color = "black", fill = "lightblue"))+
  labs(y = "Beer Factor") + labs(x = "Beer Style"),

nrow  = 1
)
```
